---
title: "R tricks"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

There have been a few specific requests for carrying out particular applications in R. We will add code to address these requests here throughout the week.

1. **Updating R, RStudio, Rpackages** 
    * If you are getting warning messages while installing packages, your version of R may be out-of-date. To keep your version of R most up-to-date, follow the directions at the [webpage linked here](http://bioinfo.umassmed.edu/bootstrappers/bootstrappers-courses/courses/rCourse/Additional_Resources/Updating_R.html).
    * **Note for Windows** : Keep in mind that if you are using the installr package for Windows, you will be installing a new package to help you. The linked page gives directions for installing this package via your console, but if you do not have internet on your computer, you'll need to [install this package from the source file](E2M2_InstallPackages.html).

2. **Correcting commas from a French dataset**
  * Many .csv files in Madagascar will have commas in place of periods for numeric entries like weights. If you are not able to import these into R correctly via the read.csv2 command, you can change them manually. Try it with the following code:
  
```{r echo=TRUE, message=TRUE, warning=TRUE, eval=FALSE}
## make up a vector where the decimals are entered as commas
comma.weights = c("56,3", "45,6", "67,8", "87,4", "42,1", "75,4")

## look at your vector of weights with commas.
comma.weights

## it is stored as a character because of the commas, which you would like to replace with periods
class(comma.weights)

## you can do this with 'gsub' in base R
comma.weights = gsub(pattern = ",", replacement = ".", x=comma.weights)

## then, turn it into a numeric vector for use in data analysis
comma.weights = as.numeric(comma.weights)

## look at the help file to explore the functions of this command and others like it further
?gsub
```
  
